Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-11 paper/paper.tex
added Fig 1C showing % IFN+
Analyzed flow data for uninfected, flu-infected,
and Sendai-infected cells and added figure
and figure supplement.

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.25\textwidth,valign=t]{figures/IFN_stochastic/RussellVenn/venn_diagram.pdf}
\hspace{0.05\textwidth}
{\bf \Large B}\includegraphics[width=0.35\textwidth,valign=t]{figures/IFN_stochastic/IFN_reporter/IFN_reporter.pdf}
\hspace{0.05\textwidth}
{\bf \Large C} \jdbcomment{ADD FIGURE PANEL}
}
\caption{
Triggering of IFN production is rare in influenza-infected cells.
{\bf (A)} Number of influenza-infected and IFN+ cells in our prior single-cell study of influenza infection of A549 cells.
The Venn diagram shows data aggregated over all samples from \citet{russell2018extreme}.
{\bf (B)} Creation of an A549 reporter cell line to efficiently identify single cells expressing IFN.
The cells are engineered to contain an IFN promoter that drives expression of a fluorescent protein and cell-surface protein amenable to MACS (magnetic-activated cell sorting).
We created reporter cell lines with both type I (IFN-$\beta$) and type III (IFN-$\lambda$) promoters (\FIGDATA[IFNrare]{reporter_sequences}).
The reporters were efficiently activated when infected with a virus known to potently induce IFN (\FIGSUPP[IFNrare]{reporter_validation}).
Expression of type I and type III IFN is highly correlated in the reporter cell lines upon infection with influenza virus (\FIGSUPP[IFNrare]{type_I_vs_III}).
{\bf (C)}
Frequency of IFN induction upon infection with the influenza virus stocks used in this paper as quantified using the reporter cell lines.
\jdbcomment{This should be a simple figure, such as a plot that just shows the fraction IFN+ among flu infected cells for the virus stocks we use, plus positive and negative controls.
Then put detailed flow data in \FIGSUPP[IFNrare]{flow}. }
}
\label{fig:IFNrare}

@@

\figsupp[Full flow cytometry data for \FIG{IFNrare}C.]
{\jdbcomment{ADD CAPTION}}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:flow}

>>>>

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.25\textwidth,valign=t]{figures/IFN_stochastic/RussellVenn/venn_diagram.pdf}
\hspace{0.02\textwidth}
{\bf \Large B}\includegraphics[width=0.32\textwidth,valign=t]{figures/IFN_stochastic/IFN_reporter/IFN_reporter.pdf}
\hspace{0.02\textwidth}
{\bf \Large C} \includegraphics[width=0.18\textwidth,valign=t]{figures/IFN_stochastic/Flow/ifn_percent.pdf}
}
\caption{
Triggering of IFN production is rare in influenza-infected cells.
{\bf (A)} Number of influenza-infected and IFN+ cells in our prior single-cell study of influenza infection of A549 cells.
The Venn diagram shows data aggregated over all samples from \citet{russell2018extreme}.
{\bf (B)} Creation of an A549 reporter cell line to efficiently identify single cells expressing IFN.
The cells are engineered to contain an IFN promoter that drives expression of a fluorescent protein and cell-surface protein amenable to MACS (magnetic-activated cell sorting).
We created reporter cell lines with both type I (IFN-$\beta$) and type III (IFN-$\lambda$) promoters (\FIGDATA[IFNrare]{reporter_sequences}).
The reporters were efficiently activated when infected with a virus known to potently induce IFN (\FIGSUPP[IFNrare]{reporter_validation}).
Expression of type I and type III IFN is highly correlated in the reporter cell lines upon infection with influenza virus (\FIGSUPP[IFNrare]{type_I_vs_III}).
{\bf (C)}
Frequency of IFN induction upon infection with the influenza virus stocks used in the single-cell studies in this paper as quantified using the IFN reporter cell line (see \FIGSUPP[IFNrare]{flow} for details).
The plot also shows uninfected cells as a negative control, and cells infected with saturating amounts of the Cantell strain of Sendai virus~\citep{strahle2006sendai} as a positive control.
The limit of detection of 0.05\% is indicated with a dashed line, and numbers show the median of three measurements.
}
\label{fig:IFNrare}

@@

\figsupp[Full flow cytometry data for \FIG{IFNrare}C.]
{Flow cytometry data for \FIG{IFNrare}C.
\jdbcomment{add details}
}
{\includegraphics[width=0.75\textwidth]{figures/IFN_stochastic/Flow/flow_plot.pdf}}
\label{figsupp:flow}
